---
title: "p8105_hw5_yl3181"
author: "Yuelin"
date: "November 2, 2018"
output: github_document
---


##Problem 1
```{r}
#Load needed libraries
library(tidyverse)
library(purrr)
```

```{r}
#Extract file name and read contents from each file
file_name = list.files("./data", full.names = TRUE)
read_file = function(name){
  read_csv(name)
}
file_content = map_df(file_name, read_file)

#Combine name with corresponding contents into one file and tidy it
file = cbind(file_name,file_content) %>%
  separate(file_name, into = c("waste1", "arm", "waste2", "subject","waste3"), sep = c(7,10,11,13)) %>% 
  select(-starts_with("waste")) %>% 
  gather(key = "week", value = "observation", starts_with("week")) %>% 
  mutate(week = as.numeric(str_replace(week, "week_", "")))
```

```{r}
#Make a spaghetti plot with two panels for better observe the difference
ggplot(file, aes(x = week, y = observation, color = subject)) + geom_line() + facet_grid(~arm)
```

As we can see in the plot: 

+ The baseline for control group and experiment group are similar;
+ The experiment group has a more rapid increase in observation values, while control group has little change in observation values


##Problem 2

```{r}
#Load and describe raw data
raw_homi = read_csv("homicide-data.csv")

#Describe data with summary statistics
knitr::kable(summary(raw_homi))
```

Raw data description:

+ The raw data contains `r nrow(raw_homi)` observations and `r ncol(raw_homi)` variables;
+ Among these variables, there are `r  sum(summary(raw_homi)[2,]==summary(raw_homi)[2,1])` character variables and `r ncol(raw_homi) - sum(summary(raw_homi)[2,]==summary(raw_homi)[2,1])` numerical variables;
+ Key variables includes `r names(raw_homi)[c(2,5:7)]`;
+ Example observations are: `r knitr::kable(raw_homi[1:3,])`
